Dynamic Transition Analysis with TIMES

### 2019-01-07 doc/2019-01-poster/poster.tex
cleanup
Former-commit-id: fec7a0d747ca9917b3e80fa055c5ef63000bec32 [formerly 6b1dc9f99b8f746b0eda8927ea41432168ad4696]
Former-commit-id: 2e3f136a089a1f9282ee0dc17a5eab5c60deae4b

\author{
       % \textbf{ENERGY ANALYSIS DIVISION}\\
       % \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions}\\
        Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
\institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
%----------------------------------------------------------------------------------------

@@

\begin{block}{Introduction}
Previous work has compared the impact of innovative energy technologies in 
various world regions using \textbf{static} scenario analyses 
\cite{chyong_chi_dynamics_2009,feng_system_2013,kikuchi_simulation-based_2017,li_energy_2010,pambudi_impact_2017,pambudi_future_2016}.  
We are simulating \textbf{dynamic} transition scenarios 
\cite{jebaraj_review_2006,pfenninger_energy_2014} aimed at optimizing energy supply to minimize carbon 
emissions in Japan to 80\% of 1990 levels by 2050, and maintaining these levels from 2050-2100. \\
Our simulation includes conventional energy sources such as \textbf{fossil fuels, nuclear energy, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}.
\end{block}

@@

         \item\textbf{Constraints:} CO$_2$ emissions, demand (+1.7\% per year).

         \item Hydropower capacity held constant

         \item All new nuclear power is based on ABWR designs.

         \item Growth rate and discrete investment size of nuclear, wind and solar is based on data and trends seen in the US, Chinese, and Japanese energy sectors.

         \item \textbf{Carbon capture and sequestration and steam reforming:} Deployed in 2030, with their costs reducing by 2050 as per projected trends.

         \item \textbf{Photocatalytic conversion:} Deployed in 2050, assumed to be cost-competitive with other H$_2$ producing technologies. \hfill \break

@@

\vspace{11mm}

@@

         \begin{alertblock}{Take Aways}
	\begin{itemize}
                \item Nuclear power has the lowest emissions intensity and it results in the most economical energy mix, despite high investment costs.

                \item Without nuclear and I$^2$CNER technology, solar and offshore wind must be deployed in a 1:2 ratio for grid resilience

                \item Cost competitive photocatalytic H$_2$ and offshore wind can replace nuclear, resulting in significantly higher system costs.

@@

%--------------------------------------------------------
% PROJECT TIMELINE
%---------------------------------------------------------
\begin{block}{Future work}
    no
\end{block}

\begin{block}{References}
        {\small\bibliographystyle{abbrv} 
        \bibliography{poster}}
\end{block}

>>>>

\author{
       % \textbf{ENERGY ANALYSIS DIVISION}\\
       % \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions}\\
        Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
\institute{University of Illinois at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
%----------------------------------------------------------------------------------------

@@

\begin{block}{Introduction}
Previous work has compared the impact of innovative energy technologies in 
various world regions using \textbf{static} scenario analyses 
\cite{kikuchi_simulation-based_2017,pambudi_impact_2017}.  
We are simulating \textbf{dynamic} transition scenarios 
\cite{pfenninger_energy_2014} aimed at optimizing energy supply to minimize carbon 
emissions in Japan to 80\% of 1990 levels by 2050, and maintaining these levels from 2050-2100. \\
Our simulation includes conventional energy sources such as \textbf{fossil fuels, nuclear, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}.
\end{block}

@@

         \item\textbf{Constraints:} CO$_2$ emissions, demand (+1.7\% per year) \cite{noauthor_electricity_2017}.

         \item Hydropower capacity held constant \cite{noauthor_energy_2018}.

         \item All new nuclear reactors are ABWRs \cite{rothwell_real_2006}.

         \item Growth rate and maximum annual increase in capacity of nuclear, wind and solar is based on data and trends seen in USA, China, and Japan. \cite{noauthor_electricity_2017,noauthor_energy_2018,eia_international_nodate,eia_monthly_2018,iea-pvps_snapshot_2018}

         \item \textbf{Carbon capture and sequestration and steam reforming:} Deployed in 2030, with its costs reducing by 2050 as per projected trends. \cite{kato_energy_2016}

         \item \textbf{Hydrogen production:} Steam reforming deployed in 2030. Photocatalytic hydrogen production deployed in 2050, assumed to be cost-competitive with other H$_2$ production technologies. \cite{kato_energy_2016} \cite{acar_comparative_2014} \hfill \break

@@

%\vspace{11mm}

@@

         \begin{alertblock}{Take Aways}
	\begin{itemize}
                \item Nuclear power has the lowest emissions intensity and it results in the most economical energy supply.

                \item Without nuclear and I$^2$CNER technology, solar and offshore wind must be deployed in a 1:2 ratio for grid resilience.

                \item Photocatalytic H$_2$ and offshore wind can meet I$^2$CNER targets in the absence of nuclear, but at significantly higher cost.

@@

%--------------------------------------------------------
% PROJECT TIMELINE
%---------------------------------------------------------
\begin{block}{Future work}
    \begin{itemize}

    \item Incorporation of more I$^2$CNER technologies.

    \item Sensitivity analysis to maximize impact of I$^2$CNER technology.

    \item Detailed cost analysis

    \item Incorporation of natural gas and/or energy storage technologies to supplement renewable energy and I$^2$CNER technology.

    \end{itemize}
\end{block}

\begin{block}{References}

        {\small\bibliographystyle{unsrt} 
        \bibliography{2019-chaube-i2cner-poster}}
\end{block}
